Forecasting the black Sigatoka development rate: A machine learning methods comparison

### 2015-11-14 Paper Sigatoka - 2015.tex
cuatro
Error en puntos y aparte corregido.  Párrafos separados en líneas más cortas para simplificar control de versiones

\section{Introduction}
The Black Sigatoka disease caused by the fungus {\it Mycosphaerella fijiensis Morelet} is the major pathological problem of banana and plantain crops in Central America, Panama, Colombia and Ecuador, as in many parts of Africa and Asia \citep{MarinVargas1995}.\\
This disease attacks the plant leaves producing a rapid deterioration of the leaf area, affects the growth and productivity of plants as the ability of photosynthesis decreases, causes a reduction in the quality of the fruit, and promotes premature maturation of bunches, which is the major cause of product losses due to this disease. \figurename $.$\ref{figura1} shows three stages of this disease.\\
Phytopathological studies point out that precipitation, temperature, relative humidity and wind are the main climatic variables that affect the development of this disease \citep{MarinVargas1995}.\\ 	 	 
\begin{figure}[h] 
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{Roya_a}
  \caption{}
  \label{fig:sfig1}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{Roya_b}
  \caption{}
  \label{fig:sfig2}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{Roya_c}
  \caption{}
  \label{fig:sfig3}
\end{subfigure}
\caption{Examples of three disease stages of the black Sigatoka. (a) Initial stage. (b) Intermediate stage, and (c) Advanced stage.} 
\label{figura1} 
\end{figure}\\
According to studies by the National Banana Corporation of Costa Rica (Corbana) made in 2013, considering on average between 53 thru 57 cycles of fungicide applications per farm, the cost per hectare per year ranged between \$1800 USD and thru \$1900 USD. This represents about 0.76 cents of the price of a box of 18.14 kilograms. Overall, this represents 10\% to 12\% of the total production cost \citet{Bresciani2015}.\\
The past and present disease development rate can in principle be used to predict its future behavior, tendencies and to determine whether particular fungicide spray schedules will be able to effectively and economically control the disease \citet{ChuangJeger1987}.\\
There are efforts to apply machine learning methods for decision-making in agriculture, including the control of crop diseases. For example, \cite{Camargo2012} present an intelligent systems for the assessment of crop disorders, \cite{Huang2010} introduce a plant virus identification method based on neural networks with an evolutionary preprocessing stage, \cite{Kim2014} summarize in their survey crop pests prediction methods using regression and machine learning approaches, while \cite{Zhao2013} present an intelligent agricultural forecasting system based on wireless sensor networks.\\
In this work, we compare four machine learning methods: support vector regression (SVR), echo state networks (ESN), ridge regression, and ordinary least squares linear regression, to predict the black Sigatoka disease development rate.\\
The main contribution of this work is a comparison between machine learning methods to forecast black Sigatoka development rate.\\

@@

Other section
I need to write

>>>>

\section{Introduction}

The Black Sigatoka disease caused by the fungus {\it Mycosphaerella
  fijiensis Morelet} is the major pathological problem of banana and
plantain crops in Central America, Panama, Colombia and Ecuador, as in
many parts of Africa and Asia \citep{MarinVargas1995}.

This disease attacks the plant leaves producing a rapid deterioration
of the leaf area, affects the growth and productivity of plants as the
ability of photosynthesis decreases, causes a reduction in the quality
of the fruit, and promotes premature maturation of bunches, which is
the major cause of product losses due to this disease. \figurename
$.$\ref{figura1} shows three stages of this disease.

Phytopathological studies point out that precipitation, temperature,
relative humidity and wind are the main climatic variables that affect
the development of this disease \citep{MarinVargas1995}.

\begin{figure}[h] 
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{Roya_a}
  \caption{}
  \label{fig:sfig1}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{Roya_b}
  \caption{}
  \label{fig:sfig2}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{Roya_c}
  \caption{}
  \label{fig:sfig3}
\end{subfigure}
\caption{Examples of three disease stages of the black Sigatoka. (a) Initial stage. (b) Intermediate stage, and (c) Advanced stage.} 
\label{figura1} 
\end{figure}

According to studies by the National Banana Corporation of Costa Rica
(Corbana) made in 2013, considering on average between 53 thru 57
cycles of fungicide applications per farm, the cost per hectare per
year ranged between \$1800 USD and thru \$1900 USD. This represents
about 0.76 cents of the price of a box of 18.14 kilograms. Overall,
this represents 10\% to 12\% of the total production cost
\citet{Bresciani2015}.

The past and present disease development rate can in principle be used
to predict its future behavior, tendencies and to determine whether
particular fungicide spray schedules will be able to effectively and
economically control the disease \citet{ChuangJeger1987}.

There are efforts to apply machine learning methods for
decision-making in agriculture, including the control of crop
diseases. For example, \cite{Camargo2012} present an intelligent
systems for the assessment of crop disorders, \cite{Huang2010}
introduce a plant virus identification method based on neural networks
with an evolutionary preprocessing stage, \cite{Kim2014} summarize in
their survey crop pests prediction methods using regression and
machine learning approaches, while \cite{Zhao2013} present an
intelligent agricultural forecasting system based on wireless sensor
networks.

In this work, we compare four machine learning methods: support vector
regression (SVR), echo state networks (ESN), ridge regression, and
ordinary least squares linear regression, to predict the black
Sigatoka disease development rate.

The main contribution of this work is a comparison between machine
learning methods to forecast black Sigatoka development rate.

@@

Revisar
Ver el tema de la Bibliografìa
